A Practical Metatheory of Bidirectional Type Synthesis for Simple Types

### 2023-06-12 tex/BiSig.tex
[ tex ] Fix Corollary 5.3 (add the condition that `t` has a synthesise mode).

\begin{corollary}[Trichotomy of Raw Terms]
  \LT{trichotomy over decidability?}
  Let $\Sigma$ be a type signature and $\Omega$ a bidirectional binding signature.
  Then, for every context $\Gamma$ and raw term $t$, exactly one of the following statements holds:
  \begin{enumerate}
    \item there exists a typing derivation of $\Gamma \vdash_{\Sigma, \Omega} t : A$ for some type $A$.
    \item there is no typing derivation of $\Gamma \vdash_{\Sigma, \Omega} t : A$ for any type $A$.
    \item $t$ cannot have a synthesis mode.
  \end{enumerate}
\end{corollary}
\begin{proof}
  Combine  \Cref{thm:term-soundness,thm:term-completeness,thm:bidirectionalisation} with \Cref{thm:bidirectional-type-synthesis},.

>>>>

\begin{corollary}[Trichotomy of Raw Terms]
  \LT{trichotomy over decidability?}
  Let $\Sigma$ be a type signature and $\Omega$ a bidirectional binding signature.
  Then, for every context $\Gamma$ and raw term $t$, exactly one of the following statements holds:
  \begin{enumerate}
    \item $t$ has a synthesis mode and there exists a typing derivation of $\Gamma \vdash_{\Sigma, \Omega} t : A$ for some type $A$.
    \item $t$ has a synthesis mode but there is no typing derivation of $\Gamma \vdash_{\Sigma, \Omega} t : A$ for any type $A$.
    \item $t$ does not have a synthesis mode.
  \end{enumerate}
\end{corollary}
\begin{proof}
  Combine  \Cref{thm:term-soundness,thm:term-completeness,thm:bidirectionalisation} with \Cref{thm:bidirectional-type-synthesis},.
